---
title: "p8105_hw1_sm5134"
author: "Sneha Mehta"
date: "2022-09-23"
output: html_document
---
```{r setup}
library(palmerpenguins)
library(tidyverse)
```


## Problem 1
Loading the `penguins` dataset:
```{r descriptive statistics}
data("penguins", package = "palmerpenguins")
View(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
This dataset describes the species, island, bill size (depth and length), flipper length, body mass, sex, and year catalogued of penguins. There are 344 entries (rows) to the dataset and 8 variables (columns). The average flipper length amongst the penguins is `mean(penguins$flipper_length_mm, na.rm = TRUE)`.

```{r plot}
ggplot(penguins, aes (x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()
ggsave("scatter.pdf", height = 4, width = 6)
```
This plot shows bill length vs flipper length of the dataset per each species of penguin.

## Problem 2
Creating the data frame: 
```{r prob2 df}
set.seed(846)

Prob2_df = tibble(
  x = rnorm(10),
  x_pos = x > 0,
  description = c("bubbly", "mighty", "quaint", "barbarious", "barbarious", "bubbly", "mighty", "mighty", "bubbly", "quaint"),
  quality = factor(c("high", "medium", "medium", "low", "high", "high", "low", "medium", "low", "low"))
  
)
view(Prob2_df)
```

Taking the mean of dataframe variables:
```{r mean}
pull(Prob2_df, var = x) %>% mean()
pull(Prob2_df, var = x_pos) %>% mean()
pull(Prob2_df, var = description) %>% mean()
pull(Prob2_df, var = quality) %>% mean()
```
Taking the mean as is worked for the random sample (x) variable and the logical variable (x_pos). 

Converting variables to numeric:
```{r conversion, results=FALSE}
pull(Prob2_df, var = x_pos) %>% as.numeric()
pull(Prob2_df, var = description) %>% as.numeric()
pull(Prob2_df, var = quality) %>% as.numeric() %>% mean()
```
Logical vector converts to 0s and 1s which explains the calculated mean of 0.6. The character variable cannot be converted. The factor variable could be converted to on a scale of 1-3, and then the mean could be taken.
